Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-06-24 WholePlotTrajectories.tex
Update WholePlotTrajectories.tex

The functional and taxonomic decoupling and the rebuttal of the IDH for
communities taxonomic structure were explained by a reorganization of
the functional redundancy within the functional traits space that
implied the incomplete resilience of communities
\citep{Trenbath1999, Elmqvist2003, Diaz2005}.

Although the functional redundancy considered in the functional space of
the whole communities did not display consistent trajectories after
disturbance, the redundancy restricted to the functional space of the
initial community clearly followed humped shaped trajectories. After
disturbance communities differently occupied the functional space,
following the observed shifts in traits trajectories and functional
composition, and the redundancy in the initial functional space
decreased according to the disturbance intensity. After 30 years the
recovery of the initial redundancy structure was consistent but remained
unachieved. It depended on infrequent species specific to old-growth
forests that were functionally and therefore underwent competitive
exclusion limiting functional similarity
\citep{Chave2004, Mayfield2010}. The persistent alteration of functional
redundancy meant a lower resilience of pre-disturbance communities and
an higher resilience disturbance-specific communities (corresponding to
lower richness and higher dominance of pioneer species) so chances to
observe self-maintained compositional changes in favor of disturbance
resistant species, lianas or epiphytes were increased after disturbance
\citep{Haddad2008, Burslem2000, Martin2013}. Communities resilience
depended on the functional redundancy structure that proved long to
recover. This decades-long recovery specifically increased the risks of
loosing cornerstone specie, with unexpected ecological consequences
\citep{Jones1994, Chazdon2003a, Diaz2005, Gardner2007}.

@@

Our study defined the decoupled functional and taxonomic trajectories of
tropical rainforests after disturbance demonstrating a rapid functional
recovery but a slower and more variable taxonomic one. Consistently with
the IDH, functional trajectories were driven after disturbance by
deterministic processes favoring pioneers and light-demanding species.
The following functional shifts entailed a re-organization of
communities functional redundancy that proved long to recover and
explained the more variable and longer taxonomic trajectories as shade
tolerant species of old-growth forests faced functional redundancy and
limiting similarity processes. The resilience of tropical forests then
proved long in the face of quite intense disturbance and did not
preclude the settling of a persistent disturbance-specific community
\citep{Gourlet-Fleury2005}. As the trajectories highlighted the
recruitment processes proved central for communities response to
disturbance and closer focus on demographical drivers of communities
response would clarify the fate of the future forests. The disturbance
range however stayed within the spectrum of selective logging, with a
forest cover remaining all along the experiment, and the response
mechanisms would probably be much different after harder disturbance.

>>>>

The functional and taxonomic decoupling as well as the rebuttal of the IDH for
communities taxonomic structure were explained by a reorganization of
the functional redundancy within the functional traits space that
implied the incomplete resilience (???) of communities
\citep{Trenbath1999, Elmqvist2003, Diaz2005}.

The functional redundancy restricted to the functional space of the
initial community clearly followed humped shaped trajectories. After
disturbance communities differently occupied the functional space,
following the observed shifts in traits trajectories and functional
composition, and the redundancy in the initial functional space
decreased according to the disturbance intensity. After 30 years the
recovery of the initial redundancy structure was consistent but remained
unachieved. ?????-> It depended on infrequent species specific to old-growth
forests that were functionally and therefore underwent competitive
exclusion limiting functional similarity
\citep{Chave2004, Mayfield2010}. ?????->The persistent alteration of functional
redundancy meant a lower resilience of pre-disturbance communities and
an higher resilience disturbance-specific communities (corresponding to
lower richness and higher dominance of pioneer species) so chances to
observe self-maintained compositional changes in favor of disturbance
resistant species, lianas or epiphytes were increased after disturbance
\citep{Haddad2008, Burslem2000, Martin2013}. ?? Not so long no? -> Communities resilience
depended on the functional redundancy structure that proved long to
recover. This decades-long recovery specifically increased the risks of
loosing cornerstone (????) species, with unexpected ecological consequences
\citep{Jones1994, Chazdon2003a, Diaz2005, Gardner2007}.

@@

Our study defined the decoupled functional and taxonomic trajectories of
tropical rainforests after disturbance demonstrating a rapid functional
recovery but a slower and more variable taxonomic one. Consistently with
the IDH, functional trajectories were driven after disturbance by
enrichment of the system with pioneers and light-demanding species.
????-> The ????following functional shifts entailed a re-organization of
communities functional redundancy that proved long to recover and
explained the more variable and longer taxonomic trajectories as shade
tolerant species of old-growth forests faced functional redundancy and
limiting similarity processes. The resilience of tropical forests then
proved long in the face of quite intense disturbance and did not
preclude the settling of a persistent disturbance-specific community
\citep{Gourlet-Fleury2005}. As the trajectories highlighted the
recruitment processes proved central for communities response to
disturbance and closer focus on demographical drivers of communities
response would clarify the fate of the future forests. ????-> The disturbance
range however stayed within the spectrum of selective logging, with a
forest cover remaining all along the experiment, and the response
mechanisms would probably be much different after harder disturbance.
